\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-11-10 analysis/paper/paper.Rmd
working on intro text

We currently have unprecedented access to publicly available hyperspectral airborne imagery at sites around the United States from the National Ecological Observatory Network (NEON) [@keller2008continental]. 
NEON-monitored sites are spread across ecoclimatic domains with a diverse array of ecosystems and land cover types including deciduous and evergreen forests, shrub/scrub and woody wetlands, mixed forest and grasslands. 
Field technicians collect field-based vegetation measurements including species observations on a semi-annual basis. 
In addition, NEON’s Airborne Observation Platform (AOP) payload carries a suite of sensors to collect both spectral and structural measurements of ecosystems [@kampe2010advances]. 
The AOP includes an imaging spectrometer which captures hyperspectral reflectance data in over 400 bands across the visible and near infrared wavelengths. 
Hyperspectral imagery is frequently used to classify species with accuracies ranging widely anywhere from 45% to 98% [@fassnacht2016review]. 
Hyperspectral data are capable of capturing reflectance variations and features with hundreds of spectral bands better than multispectral remotely sensed data with a handful to tens of bands [@awad2018forest].
Many factors influence tree species classification results including the number of species being discerned, the homogeneity of species, the density and structural complexity of the forest, and the taxonomic level of classification [@sothe2019tree]. 
Methods are often performed on small scales or in simple ecosystems, and are not successful at scaling to larger areas or different forest types **(cite)**.
Although the demand for species mapping is justified in many cases, there is also potential for both using and finding value in classifying individuals at other taxonomic levels, as explored in a recent bioacoustics study [@cramer2020chirping]. 
In the plant realm, identifying taxons at the genus level had been shown to be easier than at the species level [@tuominen2018assessment].
[@surovy2019acquisition] report that species are more successfully classified into broader categories such as spruce, pine, and broadleaf, compared to identifying individual species in mixed arrangements.

>>>>

We currently have unprecedented access to publicly available hyperspectral airborne imagery at sites around the United States from the National Ecological Observatory Network (NEON) [@keller2008continental]. 
NEON-monitored sites are spread across ecoclimatic domains with a diverse array of ecosystems and land cover types including deciduous and evergreen forests, shrub/scrub and woody wetlands, mixed forest and grasslands. 
Field technicians collect field-based vegetation measurements including species observations on a semi-annual basis. 
In addition, NEON’s Airborne Observation Platform (AOP) payload carries a suite of sensors to collect both spectral and structural measurements of ecosystems [@kampe2010advances]. 
The AOP includes an imaging spectrometer which captures hyperspectral reflectance data in over 400 bands across the visible and near infrared wavelengths. 
Hyperspectral imagery is frequently used to classify species with accuracies ranging widely anywhere from 45% to 98% [@fassnacht2016review]. 
Hyperspectral data are capable of capturing reflectance variations and features with hundreds of spectral bands better than multispectral remotely sensed data with a handful to tens of bands [@awad2018forest].
Many factors influence tree species classification results including the number of species being discerned, the homogeneity of species, the density and structural complexity of the forest, and the taxonomic level of classification [@sothe2019tree]. 
Methods are often performed on small scales or in simple ecosystems, and are not successful at scaling to larger areas or different forest types **(cite)**.
Although the demand for species mapping is justified in many cases, there is also potential for both using and finding value in classifying individuals at other taxonomic levels, as explored in a recent bioacoustics study [@cramer2020chirping]. 
In the plant realm, identifying taxons at the genus level had been shown to be easier than at the species level [@tuominen2018assessment].
In their review of over 109 publications, [@surovy2019acquisition] report that species are more successfully classified into broader categories such as spruce, pine, and broadleaf, compared to identifying individual species in mixed arrangements.
